

The problem we are interested in is broadly as follows. We are given a set
of control applications, each of which is partitioned into a set of tasks. Each of
these tasks are mapped onto different processors. The processors and hence the
tasks communicate over one or more shared buses. The tasks on each processor
are scheduled using a given scheduling policy. The messages on the shared buses
are also scheduled using a given arbitration policy.

We will use the term platform to refer to such an (i) architecture (i.e., the
processors, their connections via buses, and the mapping of tasks on the pro-
cessors and messages on the buses), as well as (ii) the different scheduling and
arbitration policies used.

Now let us consider two tasks $T_1$ and $T_2$ belonging to the same control
application, with $T_1$ and $T_2$ mapped onto different processors. $T_1$ for example
can be a sensor task and T 2 can be a controller task. T 1 and T 2 communicate
via a message stream $M$, consisting of an infinite sequence of message instances
$m_1$, $m_2$ , . . .. Assuming that $T_1$ senses at a constant periodic rate, the delay
from the instant $T_1$ senses to the time $T_2$ receives the sample depends on the

(i) processing delay suffered by $T_1$ because of the other tasks scheduled on the
same processor, and 

(ii) the delay suffered by the messages sent by $T_1$ because
of the other messages scheduled on the shared bus.

For the moment, let us focus only on the message delays. The extension to
account for delays arising from the task scheduling can be handled later in a
similar fashion.

The delays suffered by the messages will influence the performance of the
control application. Since these delays will depend on the platform (e.g., the
mapping of the tasks, scheduling policies, etc.), certain choices of the platform
will result in acceptable control performance and others will not.

In this setup, we are interested in answering questions of the form:
\begin{itemize}
 \item Given a platform and a set of control applications, does the platform meet
the control performance requirements of the different applications?
 \item  Given a set of control applications, can we synthesize a platform (or a part
of it, e.g., the scheduling policy on a bus) to meet the control performance
requirements of the different applications?
\end{itemize}

